---
title: "Batter HOF Regression"
author: "Anders Julin"
date: "7/22/2020"
output: html_document
---

```{r}
library(readxl)
batters<-read_excel("C:/Users/SEATT_000/Desktop/Summer Fun with Numbers/HOF BATTER TRAINING LIST.xlsm", col_names=TRUE)
```

Before Any Adjustments Have Been Made

```{r}
attach(batters)
initialFit<-lm(HOF~Yrs+ASG+`WAR/pos`+G+PA+AB+R+H+`2B`+`3B`+HR+RBI+SB+CS+BB+SO+IBB+GDP+SF+SH+BA+OBP+SLG+OPS+GG+SS+MVP+WS+ROY, data=batters)
summary(initialFit)
```
Adjusted R-Squared: .5917

Manual Backward Elimination
```{r}
mBackwardFit<-lm(HOF~`WAR/pos`+PA+AB+R+H+`3B`+HR+RBI+SB+CS+SO+SH+BA+SLG+SS+MVP, data=batters)
summary(mBackwardFit)
```
Adjusted R-Squared: .6379

OLSRR Backward Elimination
```{r}
ols_step_backward_p(initialFit,details = TRUE)
oBackwardFit<-lm(HOF~`WAR/pos`+PA+AB+R+H+`3B`+HR+RBI+SB+CS+SO+SH+BA+SLG+SS+MVP, data=batters)
summary(oBackwardFit)
```
Adjusted R-Squared: .6379

OLSRR Forward Elimination
```{r}
ols_step_forward_p(initialFit,details=TRUE)
oForwardFit<-lm(HOF~PA+ASG+`WAR/pos`+MVP+SS+`2B`+R+OPS+`3B`+SH+SB+CS+SO,data=batters)
summary(oForwardFit)
```
Adjusted R-Squared: .634


Going to try and improve the OLSRR backwards elimination as it has the highest adjusted r-squared and was able to correctly identify 92/99 players. More if we remove outliers and data that should not be included.